Fusion Moves for Correlation Clustering

### 2014-11-10 paper/inputs/fig_fusion.tex
cool fig

\begin{center}
\begin{figure}[ht]
\resizebox{\linewidth}{!}{
    \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

            \draw (2,2-2) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4,2-2) node[nS,fill=red!60] (n1) {$1$};
            \draw (2,0-2) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4,0-2) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

    \end{tikzpicture}
}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure*}[ht]
\resizebox{\linewidth}{!}{
    \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {proposal edge \\ labeling $\bm{x'}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {proposal edge \\ labeling $\bm{x''}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
            {proposal node \\ labeling $\bm{l'}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {proposal node \\ labeling $\bm{l''}$};

            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
            (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
            {Binary fusion \\ move problem};

            \draw (2-2,2+4) node[nS] (n0) {$0$}; 
            \draw (4-2,2+4) node[nS] (n1) {$1$};
            \draw (2-2,0+4) node[nS] (n3) {$2$}; 
            \draw (4-2,0+4) node[nS] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eCC] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eCC] node[eNS]{$w_{13}$} (n4)
            ;

            \draw (2-2,2) node[nS] (n0) {$0$}; 
            \draw (4-2,2) node[nS] (n1) {$1$};
            \draw (2-2,0) node[nS] (n3) {$2$}; 
            \draw (4-2,0) node[nS] (n4) {$3$};
            \path
                (n0) edge[eCC] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eCC] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

            % first segmentation as coloring
            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
            \path
                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
            ;

@@

            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
            {
                For all different colorings $l''$, the binary fusion move subproblem is different.
            };

            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
            {
                All these node labelings encode the same partition
            };

            \draw[black] (5,-1) -- (33,-1);

    \end{tikzpicture}
}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure*}
\end{center}
